---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

**NOTE: This is a toy package to practice the methods for creation of R packages for personal use. 

# RpackageTest

<!-- badges: start -->
<!-- badges: end -->

The goal of RpackageTest is to ...

## Installation

You can install the development version of RpackageTest from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("DannyPerez29/RpackageTest")
```

## Usage

This package contains only one function to split character vectors into its parts based on a separator.

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
(x <- "alfa,bravo,charlie,delta")
strsplit(x, split = ",")
stringr::str_split(x, pattern = ",")
```

This outputs a list with all the segments.

```{r example2}
library(RpackageTest)

str_split_one(x, pattern = ",")
```

